\documentclass{cheatsheet}

\begin{document}

\section{Piracy!}

\begin{multicols}{2}
\begin{emphbox}
\textbf{Locating a target}\\
\chrskillcheck{int}{Electronics (Sensors)}, \dice{1d} minutes.

\textbf{Estimating an approximate value of a prize}\\
\chrskillcheck[Difficult]{int}{Broker}, \dice{1d} seconds.

\textbf{Plotting an intercept course}\\
\chrskillcheck{edu}{Pilot}, \dice{1d$\times$10} seconds.

\textbf{Demanding surrender}\\
\diemod{-morale} to attempt.

\textbf{Docking with a crippled target}\\
\chrskillcheck[Routine]{dex}{Pilot}, \dice{1d} minutes.

\textbf{Setting a breaching charge}\\
\chrskillcheck{edu}{Explosives}, \dice{1d} minutes.

\textbf{Navigating an unfamiliar ship}\\
\chrskillcheck{int}{Recon}, \dice{1d} minutes.

\textbf{Finding a hidden safe}\\
\chrskillcheck[Difficult]{int}{Recon}, \dice{1d} hours.

\textbf{Overriding security systems in a vehicle}\\
\chrskillcheck[Difficult]{int}{Electronics (computers)}, \dice{1d$\times$10} minutes.

\textbf{Jumping with a stolen vehicle attached to the hull}\\
\diemod{-2/10 tons of object} to the Engineer (j-drive) check.
\end{emphbox}

\subsection{Generate a Target}

\begin{enumerate}
\item Roll on the \textbf{Prey Encounters} table (p14).
\item Roll on the \textbf{Prey Quirks} table (p19).
\item Roll on the \textbf{Prey Complications} table (p20).
\item Determine morale:\\
  merchant ship, \dice{1d+3}; armed ship, \dice{1d+6}; naval ship, \dice{1d+8}.
\item Determine encounter distance:\\
  \dice{3d $\times$ mainworld diameter} (1000km for size 0 worlds).
\item Determine direction of travel:\\
  1--3, towards mainworld; 4--5, towards jump limit; 6, other.
\item Determine how soon the ship could jump (p16).
\end{enumerate}

Example ships from \textit{High Guard} (HG) and \textit{Ships of the
  Reach} (SR):

\textbf{Traveller:} Type-S Scout (HG110); Type-J Seeker Mining Ship
(HG112); Serpent-class Scout (HG114); Asteroid Ship (HG128);
Hraye-class Scout (SR62); Kteiroa-class Seeker (SR68); or a
\textbf{Small Freighter}; or an \textbf{Unusual Vessel}; or a
\textbf{Pirate}.

\textbf{Small Freighter:} Empress Marava-class Far Trader (HG116);
Type-A2 Far Trader (HG118); Type-A Free Trader (HG120); Type-A3 Fast
Trader (SR2); Aoa'iw-class Light Trader (SR72).

\textbf{Medium Freighter:} Type-R Subsidised Merchant (HG138);
Eakhau-class Trader (SR74).

\textbf{Heavy Freighter:} Patrol Tender (SR32); Galoof-class
Megafreighter (SR48).

\textbf{Liner:} Troop Transport (HG104); Passenger Shuttle (HG106);
Type-M Subsidised Liner (HG146); Queen Elizabeth-class Liner (SR36);
Khtukhao-class Clan Transport (SR78).

\textbf{Unusual Vessel:} X-Boat (HG108); Type-K Safari Ship (HG122);
Type-Y Yacht (HG126); Type-L Lab Ship (HG134); Donosev-class Survey
Scout (HG140); Type-C Mercenary Cruiser (HG148); Herald-class Fast
Messenger (SR6); Vulture-class Salvage Hauler (SR21); Magenta-class
Repair Ship (SR29); Ihateisho-class Scout (SR64); Ktiuhui-class
Courier (SR66); Iyeliy-class Messenger (SR70); Hkiyrerao-class
Researcher (SR76); Sakhai-class Assault Transport (SR93).

\textbf{System Defence Boat:} Heavy Fighter (HG102); System Defence
Boat (TL15: HG124; TL13: HG143); or an \textbf{Escort}; or a
\textbf{Pirate}.

\textbf{Naval Patrol:} Gazelle-class Close Escort (HG130); Fleet
Courier (HG132); Crysanthemum-class Destroyer Escort (HG150);
Fer-de-lance-class Destroyer Escort (HG153); Midu Agasham-class
Destroyer (HG165); Skimkish-class Light Carrier (HG173);
Gionetti-class Light Cruiser (HG176); Ghalalk-class Armoured Cruiser
(HG180); Arakoine-class Strike Cruiser (HG188); Azhanti-class Frontier
Cruiser (HG192); Atlantic-class Heavy Cruiser (HG196); Wind-class
Strike Carrier (HG200); Antiama-class Fleet Carrier (HG204);
Kokirrak-class Dreadnought (HG208); Plankwell-class Dreadnought
(HG212); Tigeress-class Dreadnought (HG216); Planet-class Heavy
Cruiser (SR53); Aositaoh-class Cruiser (SR84); Halaheike-class Pocket
Warship (SR90).

\textbf{Escorts (convoy or naval)}: Type-T Patrol Corvette (HG136);
Leviathan-class Merchant Cruiser (HG161); P. F. Sloan-class Fleet
Escort (HG169); Fiery-class Gunship (SR12); Ritchey-class Escort
(SR44); Ekawsiykua-class Escort (SR82); or a \textbf{Pirate}.

\textbf{Pirates:} Star Ray-class Interceptor (SR4); Indigo-class
Pirate Carrier (SR8); Buccaneer-class Blockade Runner (SR10); Corsair
(SR26).

\subsection{Pirate Hunter Response}

When the target signals for help, roll for pirate hunter response:

\begin{tabularx}{\linewidth}{lX} \toprule
\dice{2d} & Response \\ \midrule
5- & No response, roll again in an hour. \\
6, 7 & A vessel launches from the starport. \\
8, 9 & A vessel launches from the starport or the hundred diameter limit. \\
10 & A vessel in orbit responds, response time is \dice{1d$+$1} hours. \\
11 & A vessel in orbit responds, response time is \dice{1d} hours. \\
12 & A vessel in orbit responds, response time is \dice{1d$\times$10} minutes. \\
13+ & A vessel in orbit responds, response time is \dice{1d$\times$5} minutes. \\
\bottomrule
\end{tabularx}

\textbf{Aslan Hierate:} \diemod{+1}\\
\textbf{Backwater:} (class E or X starport off a major route) \diemod{-2}\\
\textbf{Dangerous:} (travel advisory; or law level 3-; or unable to patrol its space) \diemod{-1}\\
\textbf{High traffic:} (class A or B starport with Ht, Hi, In, Ag, or Ri; or on a major route) \diemod{+1}\\
\textbf{Secure:} (law level 7+; or a naval base within 6 parsecs) \diemod{+1}\\
\textbf{Capital:} \diemod{+2}\\
\textbf{Naval base:} \diemod{+2}

\subsection{Morale}

Reduce morale by 1 for each critical hit and \dice{1d} for each
critical hit of severity 4+.

If morale reaches 0, the ship jumps out (if possible) or surrenders
(if not).

\subsection{Looting}

\begin{tabularx}{\linewidth}{Xll} \toprule
Item & Time Required & Skills Required \\ \midrule
Supplies & \dice{1d$\times$10} minutes & --- \\
Cargo (by hand) & \dice{1d} minutes/ton & Athletics \\
Cargo (by robot) & \dice{1d3} minutes/ton & --- \\
Cargo (by grappling arm) & 1 minute/ton & Electronics (remote ops) \\
Treasure (from safe) & \dice{1d} hours & Recon \\
Treasure (from passengers) & \dice{1d} minutes/passenger & --- \\
Equipment & \dice{1d} minutes/crewman & --- \\
Prisoners & \dice{1d} minutes/prisoner & Melee \\
Vehicles & \dice{1d$\times$10} minutes/vehicle & Electronics (computers), Pilot \\
What's Not Nailed Down & \dice{1d} hours/100 tons of ship & Athletics, Mechanic \\ \bottomrule
\end{tabularx}

\textbf{Supplies:} spare parts, food, oxygen, and other immediately
useful items.

\textbf{Cargo:} a freighter will have \dice{1d$\times$10$+$40\%} of
its cargo bay filled on average: half will be goods from the world it
has come from, or is going to, or which sell well in the Imperium or
Hierate (see below); the other half are random trade goods in 20-ton
lots.

\textbf{Treasure:} cash, previous metals, gems, jewellery, and other
easily sellable items which do not need to be fenced.  The ship's safe
will have Cr20,000/100 tons of ship.  Passengers have: Cr10,000/high,
Cr5000/mid, Cr1000/low.

\textbf{Equipment:} personal items such as weapons, armour, and
computers, which must be fenced.  Cr1000/crewman.

\textbf{Prisoners:} what it sounds like.

\textbf{Vehicles:} boats, launches, shuttles (etc) which must be
fenced.

\textbf{What's Not Nailed Down:} fully stripping the ship of all
easily transportable items, yielding 10 tons of spare parts per 100
tons of ship (only worth Cr5000 each), and all the ship's fuel.

\begin{tabularx}{\linewidth}{lXX} \toprule
\dice{2d} & Imperium -- Hierate & Hierate -- Imperium \\
2 & Advanced Weapons & Radioactives \\
3 & Live Animals & Uncommon Ore \\
4 & Luxury Goods & Luxury Goods \\
5 & Luxury Consumables & Luxury Consumables \\
6 & Spices & Textiles \\
7 & Basic Manufactured Goods & Raw Basic Raw Materials \\
8 & Biochemicals & Polymers \\
9 & Pharmaceuticals & Crystals \& Gems \\
10 & Advanced Manufactured Goods & Uncommon Raw Materials \\
11 & Advanced Machine Parts & Precious Metals \\
12 & Illegal Luxuries & Illegal Weapons \\ \bottomrule
\end{tabularx}
\end{multicols}

\begin{multicols}{2}
\section{Piracy Response Indicator (PRI)}
\begin{tabularx}{\linewidth}{lX} \toprule
\dice{2d + pri} & Action \\ \midrule
2, 3 & Vague statement.  \textsc{pri} +1. \\
4, 5 & Cr\dice{2d$\times$2000} bounty on ``any proven pirate'' alive or lawfully killed.  \textsc{pri} +1. \\
6, 7 & Cr\dice{2d$\times$5000} bounty on ``any proven pirate'' alive or lawfully killed.  \textsc{pri} +1. \\
8, 9 & Loud condemnation.  Intelligence agents start pirate hunting.  \textsc{pri} +\dice{d3}. \\
10, 11 & One small warship (eg, a patrol corvette) sent to hunt pirates for \dice{2d} months.  \textsc{pri} +\dice{d3}. \\
12, 13 & Ships totalling \dice{2d$\times$100} tons assigned to hunt pirates for \dice{4d} months.  \textsc{pri} +\dice{d3}. \\
14, 15 & Ships totalling \dice{2d$\times$200} tons assigned to hunt pirates for \dice{4d} months.  \textsc{pri} +\dice{d3}. \\
16+ & Ships totalling \dice{2d$\times$500} tons assigned to hunt pirates for \dice{4d} months.  Nearby world becomes enemy of the pirates and their known accomplices, and petitions the Imperium or other nearby worlds to mount a larger response.  \textsc{pri} +\dice{d}. \\ \bottomrule
\end{tabularx}

Piracy Response Indicator (\textsc{pri}) measures how concerned the
local worlds are, and starts at 0.

When the travellers make a strike, roll \dice{2d + pri} and consult
the actions table (above) on 12+, with the below modifiers:

\begin{tabularx}{\linewidth}{Xl} \toprule
Circumstance & \textsc{dm} \\ \midrule
Class A starport & +6 \\
Class B starport & +4 \\
Class C starport & +2 \\
Class D starport & +0 \\
Class E starport & -2 \\
Class X starport & -4 \\
``Polite'', nobody harmed, only cargo taken & -4 \\
Minimal force used, only cargo taken & -2 \\
Little force used, only nonessential items and cargo taken leaving the ship serviceable & -1 \\
Typical ``cargo raid'': some violence and threats & +0 \\
Modestly violent raid, or personal items and important components taken leaving the ship badly damaged & +1 \\
Violent raid, or ship or hostages taken, or disregard for life shown & +2 \\
Significant casualties caused, ship and/or hostages taken & +4 \\
Appallingly violent or callous actions & +6 \\
Atrocity, such as use of nerve gas against passengers & +8 \\
Allied agent in place downplaying the incident & -2 \\
Pirates have a reputation as ``good guys'' or being justified in their actions & -1 to -4 \\
Pirates have a reputation for violence and destruction & +2 \\
Pirates have an extremely bad reputation & +4 \\ \bottomrule
\end{tabularx}

\textbf{Reducing PRI:}

\begin{itemize}
\item Waiting \dice{2d} weeks reduces \textsc{pri} by 1.
\item Making a strike at least 6 parsecs away from the previous one
  reduces \textsc{pri} by \dice{d3}, on a roll of 12+ with \dice{2d +
    parsecs}.
\item Framing other pirates reduces \textsc{pri} by 1 immediately and
  again every \dice{d3} weeks, on a roll of 12+ with \dice{2d + 1} per
  100 tons of other pirate vessels captured or destroyed.
\end{itemize}

\vfill\columnbreak
\section{Standing}

\begin{tabularx}{\linewidth}{lX} \toprule
Standing & Effect \\ \midrule
20+ & All ports belonging to the power are Friendly, and the pirates gain \textsc{soc+2} within the power's territory. \\
6 to 19 & All ports belonging to the power are Tolerant. \\
-5 to 5 & No effect. \\
-20 to -6 & A bounty of Cr\dice{1000$\times$1d$\times -$standing} is placed on the pirates. \\
-40 to -21 & A patrol is dispatched to hunt down pirates in the region. \\
-40- & Assassins, naval ships, and other imperial agents are dispatched, and the attitude of all ports belonging to the power which are not already Friendly or better drop by 1 level. \\ \bottomrule
\end{tabularx}

Standing with the Imperium starts at 0.  Standing with the Aslan
Hierate starts at -5.  These are modified like so:

\textbf{Stealing Cargo:} -1 per incident in which more than Cr100,000
is stolen.

\textbf{Infamous Incidents:} \dice{-1d} per incident where the pirates
steal a large amount of cargo, capture ships, and otherwise rock the
boat.

\textbf{Atrocities:} \dice{-1d} per incident where the pirates destroy
ships, murder prisoners, or otherwise breach the code of the stars.

\textbf{Interference:} \dice{-1d} per incident where the pirates
attack imperial scouts, couriers, or convoys; damage starports or
refuelling stations; or otherwise interfere with the flow of trade.

\textbf{Heroic Deeds:} \dice{+1d} for attacking pirates or inflicting
significant damage on the other imperial power.

\textbf{Per Month Without Incident:} standing moves 1 point towards
its starting value for each month in which the pirates do nothing of
consequence

\end{multicols}

\section{Operational Considerations}
\begin{multicols}{2}
\subsection{Refuelling Times}

\begin{tabularx}{\linewidth}{lX} \toprule
Method & Fuel per Hour \\ \midrule
Starport (Class A--C) & 50 tons/FTU \\
Starport (Class D) & 25 tons/FTU \\
UNREP System & 20 tons/ton of UNREP system \\
Gas Giant Skimming & Variable \\
Liquid Water & \dice{3d3} tons/FTU \\
Ice Deposits & \dice{1d} tons/FTU \\
Sparse Ice Deposits & \dice{d3} tons/FTU \\ \bottomrule
\end{tabularx}

Each full 25 tons of fuel tankage gives 1 point of FTU.

\subsection{Stealing Ships}

\begin{tabularx}{\linewidth}{Xll} \toprule
Measure & Time Required (PWH) & Skills Required \\ \midrule
Gut a ship of security devices & \dice{1d}/10 tons of hull & Engineer or Mechanic 1 \\
Replace a ship's security devices & \dice{2d}/10 tons of hull & Engineer or Mechanic 2 \\ \bottomrule
\end{tabularx}

A ship with an active security system cannot be flown by unauthorised
personnel.

A ship gutted of security devices is obvious to any maintenance
worker, and also easy to steal as anyone can fly it.

\textbf{Gutting a ship of security devices:} after doing so, make a
\chrskillcheck[Difficult]{edu}{Engineer or Mechanic}.  On failure,
some devices remain and will reactivate at some point.

\textbf{Fit-and-replace Units:} small robots which generate \dice{1d}
PWH per point of Effect of a \chrskillcheck[Routine]{edu}{Electronics
  (remote ops)} per hour.

\textbf{Person Work Hours (PWH):} 0 if unskilled, otherwise 1 + level$\div$4.

\subsection{Transferring Cargo in Zero-G}

\begin{emphbox}
\textbf{Launching a cargo container to another ship in zero-g}\\
\chrskillcheck[Difficult]{str}{Vacc Suit} (by hand).\\
\chrskillcheck[Difficult]{dex}{Mechanic} (with a cargo crane).\\
Formidable if target is more than 100m away.

\textbf{Rigging an improvised catch system}\\
\chrskillcheck[Very Difficult]{int}{Mechanic}, made for each container.

\textbf{Repositioning to catch off-target cargo}\\
\chrskillcheck[Very Difficult]{dex}{Pilot}, \diemod{+Thrust}.
\end{emphbox}

Each container transferred by launching it in zero-g collides with the
target ship and causes damage:

\begin{itemize}
\item Without a catch system: \dice{1d}
\item With a catch system which failed: \dice{d3} (ignoring armour)
\item Off-target and not caught: \dice{Launch Effect + Pilot Effect}
\end{itemize}
\end{multicols}

\section{Crew}

\begin{multicols}{2}
See \textbf{Crewman Names} and \textbf{Crewman Quirks} tables (p11).

\begin{tabularx}{\linewidth}{lXl} \toprule
Position & Key Skills & Base Salary \\ \midrule
Pilot & Pilot, Electronics, Tactics (naval) & Cr6000 \\
Navigator & Astrogation, Electronics & Cr5000 \\
Engineer & Engineer, Mechanic & Cr4000 \\
Medic & Medic, Zero-G, Life Science, Steward & Cr4000 \\
Gunner & Gunner, Mechanic, Electronics & Cr2000 \\
Marine & Athletics, Gun Combat, Melee, Vacc Suit, Zero-G & Cr2000 \\ \bottomrule
\end{tabularx}

A \textbf{green recruit} has \diemod{+0} for key skills and \diemod{-2} for other skills.\\
An \textbf{average crewman} has \diemod{+1} for key skills and \diemod{+0} for other skills.\\
A \textbf{good pirate} has \diemod{+2} for key skills and \diemod{+1} for other skills.\\
An \textbf{excellent crewman} has \diemod{+3} for key skills and \diemod{+2} for other skills.\\
A \textbf{legendary pirate} has \diemod{+4} for key skills and \diemod{+2} for other skills.

\subsection{Morale}

Crew morale starts at \dice{1d$+$6}, and provides a \diemod{} like
other characteristics.

Make a \chrcheck{mor} when:

\begin{itemize}
\item The ship is seriously endangered
\item The crew are ordered to risk their lives
\item The crew have to endure undue hardship
\item The captain and leadership are divided or indecisive
\end{itemize}

\textbf{Damage:} a failed \chrcheck{mor} reduces morale by \dice{1d}.
Also reduce morale by 1 when:

\begin{itemize}
\item A month goes by without a division of the spoils.
\item A raid, attempt to capture cargo, or other mission fails.
\end{itemize}

\textbf{Recovery:} increase morale by 1 when:

\begin{itemize}
\item A mission with a considerable payoff is successful.
\item The crew are given shore leave and other pleasures.
\end{itemize}

\subsection{Dividing the Spoils}

King Oleb gets 10\% first.  Then, give each ordinary crewman 1 share
each (good, excellent, or legendary crewmen may have additional
shares), give the Travellers 2 shares each, and give the captain an
additional 5 shares.  Then divide the spoils by the shares.

For each crewman, make a \chrcheck[Routine]{mor}.  On failure, they
leave at the next Tolerant (or better) port.
\end{multicols}

\end{document}
